\versionLanguageStart%016
		Since August 2025, I have been unemployed and looking for work.  
		Furthermore, I have been predominantly without a permanent residence and homeless since spring 2019.  
		I like to sleep in a tent, in a car, in a trailer, with friends and family, in frost protection shelters for the homeless, or in homeless accommodations.  
		I have no desired salary in order to buy emotions with money after work; instead, I strive to be paid with emotions during work.  
		I demand that working under the influence of legal drugs such as alcohol and exorphins at the workplace not be permitted.

		If the commute or housing takes up too much time or money compared to the work, you must assume that I will sleep near the workplace in my car.  
		In this case, you can assume that I will make good use of the company kitchen.  
		If there is no kitchen in the company, I will cook in the parking lot.  
		If my work is paid reasonably well, I can afford a caravan or a motorhome.  
		If my work is paid very well, I can afford a small apartment near the company.  
		In the optimal case, you would allow me to sleep in the company with my sleeping bag.  
		Sleeping together as a team in the company strengthens team spirit, work motivation, and collaboration.  
		Once your reputation is ruined, you can work completely relaxed.

		The background is that apartments nowadays are overpriced for the quality you get.  
		It stresses me out when I work for landlords who don't really care about tenants' concerns.  
		This leads to less motivation in life and thus to lower productivity at work.  
		Currently, for example, I live in an apartment where the central ventilation for the bathroom is very loud and creates a permanent strong background noise, and I can't turn it off because it's an active central ventilation system (with a fan or similar).  
		This permanent background noise represents a burden on the psyche that, in my view, is unnecessary.  
		The building appears to be a faulty construction, and instead of being paid to endure this psychological pressure, you even have to pay extra for it.  
		I have applied for Bürgergeld (citizen's income), and the apartment will likely be paid for by Bürgergeld, which is why I can psychologically afford to live in a poor-quality apartment.  
		This changes as soon as I have to pay for the apartment myself with my own labor.

		In May 2024, I was supposed to start at Lieferando in Frankfurt.  
		I received an employment contract, but I did not get any work.  
		I waited for induction appointments and regularly asked why I was not receiving any dates.  
		On June 12, 2024, the final response came that the contract would be retroactively canceled, on the grounds that the works council had voted against my hiring.  
		It was stipulated in Article 11 of the employment contract that the employment relationship was subject to the suspensive condition that the works council must approve my hiring.  
		This led to various complications.

		In October 2025, I was supposed to start at ANT Transport GmbH in Moosburg.  
		I received an employment contract, but I did not get any work.  
		Instead, on September 26, 2025, I received notice that the contract was being terminated.  
		This led to various complications.

		To avoid this in the future, I demand a deposit of €1,000 for expenses incurred due to such complications, which will be refunded after successful completion of a probationary period of at least three months.  
		I have no reserve capital to cover expenses arising from such complications.

		Please note that my resume only lists projects/employment relationships with which I have also earned money.  
		In my private life, I have already implemented many small projects using various languages and tools (this application was almost entirely auto-generated using shell scripts, LaTeX, and Python).

		I am a flexible person and generally enjoy solving technical problems, optimizing systems, and discovering, understanding, and learning new things.  
		I am open to new challenges.  
		Thanks to my quick comprehension, I can easily familiarize myself with task areas that are unfamiliar to me.  
		Even under high workloads, I always maintain an overview and work with consistent concentration and goal orientation.  
		However, under high psychological stress, I lose my performance capacity.  
		I work without stress.  
		Under stress and time pressure, my digestive system causes problems, and I suffer significantly psychologically and health-wise.  
		Overall, I am suited for activities that require extensive training and high complexity or for tricky problems that only a few dare to tackle.

		In my many years of experience as a delivery driver for various companies such as Amazon Flex (2020–2022), Lieferando (2020–2021), Durstexpress (2020), Wolt Logistics (2024), and flaschenpost (2024), I have gathered comprehensive knowledge in the efficient delivery of packages, food, and beverages.  
		My focus has always been on punctuality, customer satisfaction, and the safe handling of goods—whether using my own car or scooter.  
		I am very familiar with the use of navigation apps, route optimization, and handling time-critical deliveries, which enables me to work calmly and goal-oriented even under high work pressure.  
		This practical experience makes me a reliable team member for your delivery service, where I would gladly contribute my flexibility and commitment.

		Through my many years of experience as a software developer, I have been able to learn a great deal about the practical workflow in software development.  
		My experience in software development consists mainly of general development, in which an existing system was differentially modified to improve it, for example by fixing bugs or adding and changing features.

		I am familiar with the most common object-oriented language concepts, software development tools (version control, IDE, CI tools), and methodologies (TDD, Scrum).

		I would be delighted to receive an invitation to negotiate an internship contract, training contract, employment contract, or project contract (as a freelancer).
\versionLanguageEnd